\begin{itemize}
\item 2020 - 11/10 (Performance) - Wexner Center For The Arts - USA / ARG - NETWORKED PERFORMANCE MUSIC with Elizabeth A Baker and the Sonic Arts Ensemble at OSU.
\item 2020 - 7/25 (Poster) -  ``Pathosonic'' presentation - NIME, Royal Birmingham Conservatory, UK
\item 2020 - 3/29 (Release) - ``basura'' (Viajero Experimental Inmóvil) and "Diciembre" (SUDA)
\item 2020 - 3/4 (Performance) - ``untitled2'' - Espacio B, Madrid, Spain
\item 2020 - 1/15 (Performance) - CLIMATE GATHERING RESIDENCY - Movement Lab at Barnard College, NYC - Residency at Barnard's Movement Lab in NYC with Livable Futures Now.
\item 2019 (Fellowship) - Postdoctoral Fellow - Ohio State University - Global Arts and Humanities Theme - Fully funded, 2-year postdoctoral research position.
\item 2019 - 12/19,22 (Performance) - Live electronics with HDDM at La Cupula - Cordoba, Argentina 
\item 2019 - 5/10 (Dissertation) - NYU - Dissertation Defense
\item 2019 (Fellowship) - Dean's Dissertation Fellowship - NYC-Berlin - NYU GSAS - 9-month.
\item 2018 - 2/3 (Publication) - ``For Young Ears'' - Open Space Magazine - New York, USA - published article.
\item 2018 - 8/3 (Performance) - ``Say Under'' - Tehran International Electronic Music Festival - Tehran, IRAN - commission by the Offborders Festival for Electroactoustic music
\item 2018 - 8/3 (Performance)  - ``Untitled'' - CUBE FEST - Virginia Tech, Blacksburg, VA 
\item 2018 - 6/10 (Performance) - ``untitled2'' - Delian Academy for New Music - Mykonos, Greece
\item 2018 (Fellowship) - Florence, Italy - NYU Global Research Initiatives - 3-month.
\item 2017 - 4/7 (Performance) - ``a.le.a'' - TALEA ENSEMBLE - Dimenna Center, NYC
\item 2017 (Grant) - ``Hearing The Self'' - Student Senators Council - Shanghai, China - NYU SSC
\item 2017 (Fellowship) - Paris, France - NYU Global Research Initiatives - 3-month.
\item 2015 (Award) - ``Ciudad Invertida'' - Selected Works mention - Fundación Destellos 
\item 2014 (Award) - ``Venas'' - Selected Works mention - Fundación Destellos 
\item 2013 (Fellowship) - MacCracken Fellowship - New York City, USA - NYU GSAS  - 5-year.
\item 2012 (Grant) - Programa Cuarto Centenario - l'Université de Montréal to study C++ - 3-month.
\item 2011 (Performance) - TSONAMI - Buenos Aires, Argentina - Improvisation with Leim Ensamble
\item 2011 (Peformance)- ``Lagos'' (orchestra) - Córdoba, Argentina - UNC Symphony Orchestra
\end{itemize}
