 \title{ Dean's Dissertation Fellowship}
 \dates{ 2018}
 \location{ NYC - Berlin}
 \employer{ NYU GSAS}
 \begin{position}
{ Thirty Dean's Dissertation Fellowships are available to eligible GSAS doctoral students in all departments who will be entering the final year of writing their dissertations.}
\end{position}
 \title{ GRI Fellowship}
 \dates{ 2018 - 2017}
 \location{ Florence (2018) - Paris (2017) }
 \employer{ NYU Global Research Initiatives }
 \begin{position}
{ Faculty and graduate student fellows at GRI Research Institutes are given office space modest administrative support one round-trip economy ticket from New York to the site and a flat-rate per-diem subsidy intended to partially defray living costs.}
\end{position}
 
\newpage

 \title{ Student Senators Council}
 \dates{ 2017}
 \location{ Shanghai - China}
 \employer{ NYU SSC}
 \begin{position}
{ The Student Senators Council (SSC) with the generous assistance of the Senior Vice-Provost for Research has established a fund to support students traveling to conferences to present a project.}
\end{position}
 \title{ Selected Works}
 \dates{ 2014 - 2015}
 \location{ La Plata - Buenos Aires}
 \employer{ Fundación Destellos}
 \begin{position}
{ The works ``Ciudad Invertida'' for Trombone Duo, Live Video and Electronics (2015), and ``Venas'' for Bass Clarinet, Live Video and Electronics (2014) were consecutively awarded the ``Selected Works'' title by this reknowned Argentinian Foundation. }
\end{position}
 \title{ MacCracken Fellowship}
 \dates{ 2013}
 \location{ New York City}
 \employer{ NYU GSAS}
 \begin{position}
{ A four- or five-year award term. A scholarship for full tuition and registration and services fees for courses required for the degree. Full coverage of the premiums for mandatory NYU student health insurance for an individual under the NYU comprehensive plan. A nine-month academic-year stipend for living expenses. Some departments offer either a stipend or research assistantship. The minimum stipend amount in 2017-18 is USD 27,526. A one-time Dean’s Supplementary Fellowship Grant of USD 1,000 that may be used at the student’s discretion.}
\end{position}
 \title{ Programa Cuarto Centenario}
 \dates{ 2012}
 \location{ Montréal - Canada}
 \employer{ Universidad Nacional de Córdoba}
 \begin{position}
{ Exchange at l'Université de Montréal to take undergraduate introductory courses on the C++ programming language.}
\end{position}
 \title{ Orchestral Performance}
 \dates{ 2011}
 \location{ Córdoba - Argentina}
 \employer{ Universidad Nacional de Córdoba}
 \begin{position}
{ The work for large orchestra ``Lagos'' was selected for premiere by Gonzalo Bustos and the Symphony Orchestra of the National University of Córdoba.}
\end{position}