\title{ PdCon16\url{~} }
\location{ New York City }
\employer{ Pure Data Convention }
\dates{ 2016 }
\begin{position} 
New York University in collaboration with the Stevens Institute of Technology, hosted the 5th International Pure Data Convention in New York City on November 16-20th, 2016. I worked as assistant, organizer, webmaster, and graphic designer.
\end{position}

\title{ Waverly Project }
\employer{ New Music Organization}
\location{ NYU GSAS}
\dates{ 2013-2017 }
\begin{position}
Waverly Project was a platform for presenting the output of composers at NYU in any form. The mission of the project was to present exciting new music from the city, to offer rising artists a NYC premiere, and to forge new, international links between a generation of emerging musicians. The project started in collaboration with NYU composer and colleague Ioannis Angelakis in 2013 and kept on going under different direction and new collaborations with other colleagues throughtout our PhD coursework years until 2017.
\end{position}

\title{ Proyecto[Red]Ensamble }
\location { Universidad Nacional de Córdoba }
\employer{ Contemporary Music Ensemble}
\dates{ 2010-ongoing }
\begin{position} 
Proyecto[Red]Ensamble is a network of musicians, composers, visual artists, dancers, and performers which started in early 2010 in collaboration with UNC composer and colleague Pablo Behm. The project aims to bring to the concert hall (and outside of it) new collaborative and experimental works. It is a non-profit organization offering to forge a diverse, interdisciplinary, and non-hierarchical view of art production in the city of Córdoba, Argentina.
\end{position}

\title{ Bienal Composición Córdoba }
\employer{ Music Composition Biennale}
\dates{ 2010-2012-2015 }
\begin{position} 
This international biennale is a center for music composition thought, from broad aspects such as teaching, theory, performance, among others. It was created by Professor José Halac and over the years I have worked as assistant, webmaster, graphic designer and organizer.
\end{position}